---
title       : Applying polynomial regression on car stopping distance by speed
subtitle    : 
author      : Heping Zheng
job         : science
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [mathjax, bootstrap, quiz]            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## The cars dataset

1. From the datasets package
    ```{r, echo=FALSE}
    library(datasets)
    data(cars)
    str(cars)
    ```

2. Data is consists of 50 records of 2 columns
3. Explanation of variables
    a. dist: stopping distance (in feet)
    b. speed: speed of car (in M.P.H.)

    ```{r, echo=FALSE}
    head(cars, 3)
    ```


--- .class #id 

## The scatterplot of the cars dataset

```{r, echo=FALSE}
plot(cars, xlab = "Speed (mph)", ylab = "Stopping distance (ft)",
         las = 1, xlim = c(0, 30))
```

---

## Polynomial fittings with degree from 1 to 6

```{r, echo=FALSE}
plot(cars, xlab = "Speed (mph)", ylab = "Stopping distance (ft)",
    las = 1, xlim = c(0, 25))
d <- seq(0, 25, length.out = 200)
for(degree in 1:6) {
  fm <- lm(dist ~ poly(speed, degree), data = cars)
  assign(paste("cars", degree, sep = "."), fm)
  lines(d, predict(fm, data.frame(speed = d)), col = degree)
}
legend(x=100, legend=paste("degree = ", 1:6, sep=""), col = 1:6, lwd=2)
```

--- &radio
## Question 1


What is the best polynomial model?

1. _1_
2. 2
3. 3
4. 4

*** .hint
The simplest model with significant p-value is the best polymonial model

*** .explanation
```{r, echo=FALSE}
anova(cars.1, cars.2, cars.3, cars.4)
```
All higher degree models are not significant, therefore the first order linear model is the best model



